AIS

### 2023-08-08 02_AIS.Rmd
added note to update AIS directory
Update 02_AIS.Rmd
added Taiki's workflow to this

---
title: "AIS"
author: "Marina Bozinovic"
date: "2023-04-11"
output: html_document
---
```{r}
#Required Packages

library(tidyverse)
library(sf)
library(gganimate)
#install.packages("remotes")
#remotes::install_github("skgrange/gissr")
#devtools::install_github("skgrange/gissr")
library(gissr)
```

@@

# Need to add more AIS dates in data folder
AISlist <- list.files(path = paste0("data-raw/"), pattern = "AIS_", recursive = TRUE)

@@

```{r}
# Plot showing 10km buffer around drift 8
#tmap_mode("plot")
#tm_shape(buff) + tm_symbols(col = "blue", border.col = NA) +
#  tm_shape(trk) + tm_dots(col = "red")
```

plots
```{r}
# Plot
ggplot(tracks_SS_08, aes(x = long, y = lat.x)) + geom_point() 
 + geom_sf(data = bbox8, aes(col = "red"))

# Plot showing AIS bounding box around drift 8 tracks
ggplot() + geom_sf(data = trk_AIS_sf, color = "red")
ggplot() + geom_sf(data = buff[lgth,] ,color = "red")

ggplot() +
  geom_sf(data = calif) + coord_sf(default_crs = sf::st_crs(4326)) + theme_bw()
 # geom_sf(data = AIS_sf)

p <- ggplot() + geom_sf(data = buff, mapping = aes(x=Longitude,y=Latitude)) +
  geom_point(data = AIS_within_buff, mapping = aes(x=LON,y=LAT, group = VesselName), color = "red")

anim <- p +
  transition_reveal(along = BaseDateTime)+
  ease_aes('linear')+
  #shadow_wake(0.1) +
  ggtitle("Date: {frame_along}")

animate(anim, nframes = 180, fps = 3)
```

>>>>

---
title: "AIS"
author: "Marina Bozinovic"
date: "2023-04-11"
output: html_document
---

#Introduction
AIS download from Marine Cadastre and match to buoy datasets.

Required Packages
```{r}
library(PAMscapes)
library(tidyverse)
```

@@

##### Need to add more AIS dates to D: DRIVE!!!
AISlist <- list.files(path = paste0("data-raw/"), pattern = "AIS_", recursive = TRUE)

@@

-----------------------
From Taiki's AIS Workflow

```{r}
marcadFiles07 <- downloadMarCadAIS(tracks_SS_07, outDir = "D:/AIS", overwrite = FALSE, unzip = TRUE)
```

Subset to US West Coast
```{r}
subsetMarCadAIS(inDir="D:/AIS", outDir="D:/AIS/AIS_West", name='West_', 
                latRange=c(20,50), lonRange=c(-140,-110),
                overwrite=FALSE, progress=TRUE)
```
Now read in only ais points that come in contact with buoys.
```{r}
ais_near_07 <- readLocalAIS(tracks_SS_07, aisDir="D:/AIS/AIS_West", distance=10e3) %>%
   filter(vesselLength >= 100)  #remove vessels under 100m in length
View(ais_near_07)

gpsClose <- addAIS(tracks_SS_07, ais_near_07, interpType = 'close', interpTime = 120)
gpsNone <- addAIS(tracks_SS_07, ais_near_07, interpType = 'none')
gpsAll <- addAIS(tracks_SS_07, ais_near_07, interpType = 'all', interpTime = 120)

## Using PRE-ROUNDED dataset to try out
ais_near_raw7 <- readLocalAIS(tracks7, aisDir = "D:/AIS/AIS_West", distance=10e3) %>%
   filter(vesselLength >= 100)  #remove vessels under 100m in length
gpsClose_raw7 <- addAIS(tracks7, ais_near_raw7, interpType = 'close', interpTime = 120)
```

Plot
```{r}
ggplot() +
    geom_path(data=tracks_SS_07, aes(x=Longitude, y=Latitude), col='black') +
    geom_path(data=ais_near_07, aes(x=Longitude, y=Latitude, group=factor(MMSI), col=inDist)) +
    xlim(min(tracks_SS_07$Longitude), max(tracks_SS_07$Longitude)) +
    ylim(min(tracks_SS_07$Latitude), max(tracks_SS_07$Latitude))

baseGps <- ggplot(data=tracks7, aes(x=Longitude, y=Latitude), col='black') +
    geom_path() +
    xlim(min(tracks7$Longitude), max(tracks7$Longitude)) +
    ylim(min(tracks7$Latitude), max(tracks7$Latitude))

baseGps + geom_path(data=gpsClose_raw7, aes(x=shipLong, y=shipLat, group=factor(MMSI), color=shipDist < 10e3)) +
     geom_point(data=gpsClose_raw7, aes(x=shipLong, y=shipLat, color=shipDist < 10e3), size = 0.1) +
    ggtitle('CloseInterp')

# Viewing only ships within 10 km of buoys.
close2ships7 <- gpsClose %>% filter(shipDist < 10e3)
```
